A Minimal Book Example

### 2020-02-18 manuscript/drafts/manuscript.Rmd
updated analysis plan

---
title: "parameters"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: pdf_document
bibliography: asreview.bib
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

```{r}
# configurations table 
tab <- lapply(words, FUN = function(x) paste(x, collapse = ", "))
tab <- do.call(rbind, tab)
colnames(tab) <- c("Configurations")

```

```{r}
# combinations table
combins <- expand.grid(params) %>%
  arrange(model, feature_extraction)

# rows to drop
droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
combins <- combins[!droprows, ]
``` 
# Introduction

## The problem
## Current solutions
Workload savings 30-70 percent, at a loss of 5% of relevant studies [@Omara-Eves2015].

@@

- a model
- a query strategy
- a balance strategy (fixed)
- a feature extraction strategy
- number of training data

The goal: 
Use these inputs to predict relevance of papers.

Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.

@@

The balance strategy

```{r}
kable(tab, "latex", booktabs = TRUE) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(2, width = "30em") 
```
### Feature Extraction Strategies 
split_ta = overall hyperparameter

@@

# Appendix A - combinations

```{r}
names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy", "Training data [included/excluded]")
combins %>%
  kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
  kable_styling(latex_options = c("repeat_header")) 
```

>>>>

---
title: "Manuscxript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: pdf_document
bibliography: asreview.bib
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

```{r}
# configurations table 
tab <- lapply(words, FUN = function(x) paste(x, collapse = ", "))
tab <- do.call(rbind, tab)
# remove row training data (28.02)
colnames(tab) <- c("Configurations")
tab <- tab[-4,]
```

```{r}
# combinations table
params[[4]] <- NULL # remove training data
combins <- expand.grid(params) %>%
  arrange(model, feature_extraction)

# rows to drop
droprows <- combins$model == "nb" & combins$feature_extraction != "tfidf"
combins <- combins[!droprows, ]
``` 
# Analysis strategy
Goal: evaluate performance of different models of the ASReview tool.

@@

<!-- - a model -->
<!-- - a query strategy -->
<!-- - a balance strategy -->
<!-- - a feature extraction strategy -->

```{r}
kable(tab, "latex", booktabs = TRUE, col.names = "Configurations") %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(2, width = "30em") 
```

Use these inputs to predict relevance of papers.

## Stage 1: hyperparameter optimization
We are going to test 5 models on 5 different datasets.

### Datasets

#### ptsd
#### ace
#### hall 
#### nagtegaal - van PhD van Lars
#### medische van Jan

### Models
- Naive Bayes 
- Random Forests
- Support Vecor Machine 
- Logistic Regression
- Dense Neural Network

Or, more specific:

```{r}
tabbie <-
  combins %>%
  filter(query_strategy == "max",
         feature_extraction %in% c("doc2vec", "tfidf") & model %in% c("dense_nn","svm", "nb", "rf", "lr")) %>%
  select(-query_strategy)

tabbie <- tabbie[c(1,3,5,6,9),]
row.names(tabbie) <- NULL
tabbie %>%
  kable(col.names = names(words)[1:3], format = "latex")
```

The other parameters remain fixed over the 5 models:

- Query Strategy = max
- Balance Strategy = triple
- n_instances=10 (number of papers each query)
- n_prior_included = 5
- n_prior_excluded = 5

### Hyperparameters
Every model has its own set of hyperparameters:

### Optimization
The hyperparameters are optimized on the 5 datasets in three different ways:

- 1 on 1: maximum performance 
- 4 on 1: cross-validation 
- 5 on 1: more data = more better?

This results $(5+5+1)*5$ sets of hyperparameters.

## Stage 2: simulation
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

### Outcomes 
Several metrics are used to compare performance of different models over datasets,

| Dataset   |   | Naive Bayes | Random Forests | Support Vector Machine | Logistic Regression | Dense Neural Network |  
| --------- | - | --- | --- | --- | --- | ---|
| ptsd      |   | ?   |     |     |    |     | 
| ace       |   | ?   |     |     |    |     | 
| hall      |   | ?   |     |     |    |     | 
| nagtegaal |   | ?   |     |     |    |     | 
| ....      |   | ?   |     |     |    |     |

? How to compare outcomes of 3 different optimization strategies?

# Appendix A - list of definitions
Machine learning algorithms cannot predict the relevance of abstracts from the raw texts as they are. 
The content of the texts needs to be transformed into numerical representations. The processs of transforming texts to numerical feature vectors is called word embeddings.

@@

### Feature Extraction Strategies 
split_ta = overall hyperparameter

@@

# Appendix B - combinations

```{r}
names(combins) <- c("Model", "Query Strategy", "Feature extraction strategy") #, "Training data [included/excluded]")
combins %>%
  kable(row.names = FALSE, format = "latex", longtable = TRUE, booktabs = TRUE) %>%
  kable_styling(latex_options = c("repeat_header")) 
```

### 2020-02-18 manuscript/test/_book/bookdown-demo.tex
updated analysis plan

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{book}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={A Minimal Book Example},
  pdfauthor={Yihui Xie},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{A Minimal Book Example}
\author{Yihui Xie}
\date{2020-02-12}

@@

{
\setcounter{tocdepth}{1}
\tableofcontents
}
\hypertarget{frontpage}{%
\chapter{Frontpage}\label{frontpage}}

This is my thesis project.

\hypertarget{intro}{%
\chapter{Introduction}\label{intro}}

You can label chapter and section titles using \texttt{\{\#label\}} after them, e.g., we can reference Chapter \ref{intro}. If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \ref{methods}.

Figures and tables with captions will be placed in \texttt{figure} and \texttt{table} environments, respectively.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{par}\NormalTok{(}\DataTypeTok{mar =} \KeywordTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{4}\NormalTok{, }\FloatTok{.1}\NormalTok{, }\FloatTok{.1}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(pressure, }\DataTypeTok{type =} \StringTok{\textquotesingle{}b\textquotesingle{}}\NormalTok{, }\DataTypeTok{pch =} \DecValTok{19}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{figure}

{\centering \includegraphics[width=0.8\linewidth]{bookdown-demo_files/figure-latex/nice-fig-1}

}

\caption{Here is a nice figure!}\label{fig:nice-fig}
\end{figure}

Reference a figure by its code chunk label with the \texttt{fig:} prefix, e.g., see Figure \ref{fig:nice-fig}. Similarly, you can reference tables generated from \texttt{knitr::kable()}, e.g., see Table \ref{tab:nice-tab}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\OperatorTok{::}\KeywordTok{kable}\NormalTok{(}
  \KeywordTok{head}\NormalTok{(iris, }\DecValTok{20}\NormalTok{), }\DataTypeTok{caption =} \StringTok{\textquotesingle{}Here is a nice table!\textquotesingle{}}\NormalTok{,}
  \DataTypeTok{booktabs =} \OtherTok{TRUE}
\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:nice-tab}Here is a nice table!}
\centering
\begin{tabular}[t]{rrrrl}
\toprule
Sepal.Length & Sepal.Width & Petal.Length & Petal.Width & Species\\
\midrule
5.1 & 3.5 & 1.4 & 0.2 & setosa\\
4.9 & 3.0 & 1.4 & 0.2 & setosa\\
4.7 & 3.2 & 1.3 & 0.2 & setosa\\
4.6 & 3.1 & 1.5 & 0.2 & setosa\\
5.0 & 3.6 & 1.4 & 0.2 & setosa\\
\addlinespace
5.4 & 3.9 & 1.7 & 0.4 & setosa\\
4.6 & 3.4 & 1.4 & 0.3 & setosa\\
5.0 & 3.4 & 1.5 & 0.2 & setosa\\
4.4 & 2.9 & 1.4 & 0.2 & setosa\\
4.9 & 3.1 & 1.5 & 0.1 & setosa\\
\addlinespace
5.4 & 3.7 & 1.5 & 0.2 & setosa\\
4.8 & 3.4 & 1.6 & 0.2 & setosa\\
4.8 & 3.0 & 1.4 & 0.1 & setosa\\
4.3 & 3.0 & 1.1 & 0.1 & setosa\\
5.8 & 4.0 & 1.2 & 0.2 & setosa\\
\addlinespace
5.7 & 4.4 & 1.5 & 0.4 & setosa\\
5.4 & 3.9 & 1.3 & 0.4 & setosa\\
5.1 & 3.5 & 1.4 & 0.3 & setosa\\
5.7 & 3.8 & 1.7 & 0.3 & setosa\\
5.1 & 3.8 & 1.5 & 0.3 & setosa\\
\bottomrule
\end{tabular}
\end{table}

You can write citations, too. For example, we are using the \textbf{bookdown} package (Xie \protect\hyperlink{ref-R-bookdown}{2020}) in this sample book, which was built on top of R Markdown and \textbf{knitr} (Xie \protect\hyperlink{ref-xie2015}{2015}).

\hypertarget{literature}{%
\chapter{Literature}\label{literature}}

Here is a review of existing methods.

\hypertarget{methods}{%
\chapter{Methods}\label{methods}}

We describe our methods in this chapter.

@@

\hypertarget{methods-1}{%
\section{Methods}\label{methods-1}}

@@

\hypertarget{appendix-a}{%
\chapter{Appendix A}\label{appendix-a}}

We have finished a nice book.

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-xie2015}{}%
Xie, Yihui. 2015. \emph{Dynamic Documents with R and Knitr}. 2nd ed. Boca Raton, Florida: Chapman; Hall/CRC. \url{http://yihui.name/knitr/}.

\leavevmode\hypertarget{ref-R-bookdown}{}%
---------. 2020. \emph{Bookdown: Authoring Books and Technical Documents with R Markdown}. \url{https://github.com/rstudio/bookdown}.
\end{cslreferences}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{book}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={A Minimal Book Example},
  pdfauthor={Yihui Xie},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\title{A Minimal Book Example}
\author{Yihui Xie}
\date{2020-02-18}

@@

{
\setcounter{tocdepth}{1}
\tableofcontents
}
\hypertarget{thesis-ferdinands}{%
\chapter{thesis Ferdinands}\label{thesis-ferdinands}}

Goal: evaluate performance of different models of the ASReview tool.

\hypertarget{stage-1-hyperparameter-optimization}{%
\subsection{Stage 1: hyperparameter optimization}\label{stage-1-hyperparameter-optimization}}

We are testing 5 models on 5 different datasets.

Every model has its own set of hyperparameters.
The hyperparameters are optimized on the 5 datasets in three different ways:

\begin{itemize}
\tightlist
\item
  1 on 1: maximum performance
\item
  4 on 1: cross-validation
\item
  5 on 1: more data = more better?
\end{itemize}

This results \((5+5+1)*5\) sets of hyperparameters.

\hypertarget{stage-2-simulation}{%
\subsection{Stage 2: simulation}\label{stage-2-simulation}}

for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed. From these \(5*5*3=75\) simulation studies, performance of the different models is evaluated.

\hypertarget{scripts}{%
\section{Scripts}\label{scripts}}

\begin{itemize}
\tightlist
\item
  simulatie:
\item[$\square$]
  script die optimalisatie genereert (config files.)
\item[$\square$]
  script die \texttt{.ini}'s voor simulatie genereert.
\end{itemize}

\hypertarget{strategy}{%
\chapter{Analysis strategy}\label{strategy}}

\hypertarget{datasets}{%
\section{Datasets}\label{datasets}}

\begin{itemize}
\tightlist
\item
  ptsd
\item
  ace
\item
  hall
\item
  nagtegaal - van PhD van Lars
\item
  medische van Jan
\end{itemize}

\hypertarget{models}{%
\section{Models}\label{models}}

(input table here?)

\begin{itemize}
\tightlist
\item
  Naive Bayes
\item
  Random Forests
\item
  Support Vecor Machine (doc2vec)
\item
  Logistic Regression
\item
  Dense Neural Network (doc2vec)
\end{itemize}

The other parameters remain fixed over the 5 models:

\begin{itemize}
\tightlist
\item
  Feature extraction = tf-idf
\item
  Query Strategy = max
\item
  Balance Strategy = triple
\item
  n\_instances=10 (number of papers each query)
\item
  n\_prior\_included = 5
\item
  n\_prior\_excluded = 5
\item
  mix\_ratio = 0.95 (95\% max, 5\% random)
\end{itemize}

\hypertarget{hyperparameters}{%
\section{Hyperparameters}\label{hyperparameters}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{list-of-definitions}{%
\chapter{List of definitions}\label{list-of-definitions}}

### 2020-02-18 manuscript/test/index.Rmd
updated analysis plan

# Frontpage
This is my thesis project.

>>>>

# thesis Ferdinands
Goal: evaluate performance of different models of the ASReview tool.

### Stage 1: hyperparameter optimization
We are testing 5 models on 5 different datasets.

Every model has its own set of hyperparameters.
The hyperparameters are optimized on the 5 datasets in three different ways:

- 1 on 1: maximum performance 
- 4 on 1: cross-validation 
- 5 on 1: more data = more better?

This results $(5+5+1)*5$ sets of hyperparameters.

### Stage 2: simulation
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

## Scripts 
  - simulatie:
- [ ] script die optimalisatie genereert (config files.)
- [ ] script die `.ini`'s voor simulatie genereert.
